Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-14 talk/pepm2011/paper.tex
mention self

@@

XXX cite SELF paper for the type propagation effects

>>>>

The original SELF JIT compiler \cite{chambers_efficient_1989} used an algorithm for
forward-propagating the types of variables as part of its optimizations. This
makes it possible to remove all type checks on a variable but the first one.
The optimization does not deal with removing the full object, if it is
short-lived, but the type check removals are similar to what our optimization
achieves.

@@
